---
title: "Data Analysis"
author: "Team 7"
date: "December 10, 2021"
output:
  html_document:
    df_print: paged
    toc: true
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(data.table)
library(dplyr)
library(ggplot2)
library(ggmap)
library(maptools)
library(maps)
library(sf)
library(stringr)
library(stargazer)
library(ggpubr)

df <- fread("data/Attitude+Survey+for+Web+App_December+9,+2021_11.53.csv") # Change this to the most recent survey 

```

## Data Cleaning
```{r}
# removing the header
df = df[c(-1,-2),] 
# Renaming columns
df <- df%>%rename(Age=` `,Gender=Q2,Education=Q3,subgroup = FL_49_DO)
# Keeping only the finished surveys
df_finished = df%>%filter(Finished == 'True') 
# making the blank cells to be the control group
df_finished$subgroup[df_finished$subgroup == ""] <- 'Control' 
df_finished$group<- ifelse(grepl('^Treatment', df_finished$subgroup), 'Treatment', 'Control')
# extract out the dollar values
df_finished$willing_to_pay <- str_extract(df_finished$Q16, '\\$(\\d+)')
# Remove the dollar sign
df_finished$willing_to_pay <- (gsub("\\$", "", df_finished$willing_to_pay)) 
# Add 0 to the NA  values
df_finished$willing_to_pay[is.na(df_finished$willing_to_pay)] <- 0
#Create binary outcome
df_finished$is_willing_to_pay<- ifelse(df_finished$willing_to_pay>0,1,0)
#Create binary indicators for age
df_finished$equal_over35<- ifelse(df_finished$Age=="35 or more than 35",1,0)
df_finished$equal_over30<- ifelse(df_finished$Age=="30-34" | df_finished$Age=="35 or more than 35",1,0)
df_finished$hasGraduateDegree<- ifelse(df_finished$Education=="Master's degree, Ph.D, or higher",1,0)
# Select just the columns needed
df_finished <- df_finished %>% 
              select(ResponseId,Age,Gender,Education,subgroup,group,equal_over35,
                     equal_over30,hasGraduateDegree,willing_to_pay,is_willing_to_pay)%>%
              mutate(willing_to_pay = as.numeric(willing_to_pay))
```


```{r}
control_group = df_finished%>%filter(group == "Control")
treatment_group = df_finished%>%filter(group == "Treatment")
```
## Survey Metadata

+ We have collected so far `r nrow(df)` surveys.
+ These include `r nrow(df_finished)` finished surveys.
+ We have `r nrow(control_group)` subjects in the control group and `r nrow(treatment_group)` subjects in the treatment groups

## Where Survey Participants Are Coming From 

```{r}
map_df <- df%>%select(LocationLatitude,LocationLongitude)
mapWorld <- borders("world", colour="gray50", fill="white")
mp <- ggplot() + mapWorld
mp + geom_point(data = map_df, aes(x =as.numeric(LocationLongitude), y=as.numeric(LocationLatitude)))
  
```

## Data Exploroation 
We collected `r nrow(df)` responses from our survey, and this included `r nrow(df_finished)` completed surveys. As you can see from the figure (map) the majority of respondents are from the United States. We also received several responses from individuals living in India.

Our treatment group consisted of `r nrow(treatment_group)` subjects, and the control group had `r nrow(control_group)` subjects. Figure (figure #) shows the distribution of the treatment and control group, and figure (figure #) shows the distribution of the `r nrow(treatment_group)` treatment subjects across the three treatment groups.
As evident from this figure, our treatment group has more subjects compared to the control group, and this was intentional and part 
of our survey design. Since we had three sub groups within our treatment, we wanted to ensure that each of the 
subgroups have an adequate number of subjects. 

The sample we collected included `r df_finished%>%filter(Gender=='Female')%>%nrow()` female respondents, `r df_finished%>%filter(Gender=='Male')%>%nrow()` male subjects and `r df_finished%>%filter(Gender=="Non-binary / third gender")%>%nrow()` that identified as Non-binary / third gender

Most of the respondents in our survey had completed a four-year college degree. In addition to that, over 50 individuals had 
completed a Masters Degree or a Ph.D. The age distribution shown in figure (figure#) shows that a most of the subjects were between the age of 25 and 29 followed by those who are 35 or more. 


### Distribution among Treatment Groups and Control Groups

```{r}
group_dist<- ggplot(data = df_finished)+
  aes(x = factor(group),fill = group)+
  geom_bar(stat = "count")+ggtitle("Subject Distribution")+xlab("Group")
```

```{r}
subgroup_dist<- ggplot(data = df_finished)+
  aes(x = factor(subgroup),fill = group)+
  geom_bar(stat = "count")+ggtitle("Subject Distribution By Sub Groups")+xlab("SubGroup")
```

```{r}
ggarrange(group_dist, subgroup_dist,
          labels = c("A", "B"),
          ncol = 1, nrow = 2)
```



### Demographic Distribution 

#### Gender
```{r}
ggplot(data = df_finished)+
aes(x = factor(df_finished$Gender),fill = Gender)+
geom_bar(stat = "count")+ggtitle("Gender")
```


#### Education
```{r}
ggplot(data = df_finished)+
  aes(x = factor(df_finished$Education),fill = Education)+
  geom_bar(stat = "count")+ggtitle("Education")+coord_flip()
```

#### Age Distribution
```{r}
ggplot(data = df_finished)+
  aes(x = factor(df_finished$Age),fill= Age)+
  geom_bar(stat = "count")+ggtitle("Age")+xlab("Age Groups")
```


# Testing to see if there is a Association between Gender and being in the control group 
```{r}
# Is the Gender distribution in the treatment and control group the same or different
# Ran a Fisher Test since the  the smallest expected frequency is lower than 5
df <- table(df_finished$Gender, df_finished$group)
fisher.test(df)
# seems like there is an association between gender and being the control or treatment group

```

# Comparing the Control and Treatment group willingness to pay

## Between The Control Group and All Treatment Groups
```{r}
(group_summary <- df_finished%>%
                  group_by(group)%>%summarize(`avg willingness in dollars`=mean(willing_to_pay),
                                              `sd willing to pay in dollars` = sd(willing_to_pay),
                                              lower = t.test(willing_to_pay)$conf.int[1],
                                              upper = t.test(willing_to_pay)$conf.int[2]))

```
```{r}
# plotting the values 
ggplot(data = group_summary,
       aes(x=group,y=`avg willingness in dollars`,fill = group))+geom_bar(stat = 'identity')+
       ylim(0,3)+ylab("avg willingness to pay in dollars ($)")+
       geom_errorbar(aes(ymin=lower, ymax=upper), 
                width=.2,                    # Width of the error bars
                position=position_dodge(0.9))+
       ggtitle ("Average Willingness to pay between all overall Treatment and Control")

```







## Betweem The Control and Treatment Sub Groups

```{r}

(sub_group_summary <-  df_finished%>%
                      group_by(subgroup)%>%
                      summarize(`avg willingness in dollars`=mean(willing_to_pay),
                                `sd willing to pay in dollars` = sd(willing_to_pay),
                                lower = t.test(willing_to_pay)$conf.int[1],
                                upper = t.test(willing_to_pay)$conf.int[2]))

```


```{r}

ggplot(data = sub_group_summary,
       aes(x=subgroup,y=`avg willingness in dollars`,fill = subgroup))+geom_bar(stat = 'identity')+
       ylim(0,3)+ylab("avg willingness to pay in dollars ($)")+
       geom_errorbar(aes(ymin=lower, ymax=upper), 
                width=.2,                    # Width of the error bars
                position=position_dodge(0.9))+
       ggtitle ("Average Willingness to pay between sub groups")

```









## Regression Analysis
```{css, echo = FALSE}

table, td, th {
  border: none;
  padding-left: 10px;
  padding-right: 10px;
  margin-left: auto;
  margin-right: auto;
  margin-top: 1em;
  margin-bottom: 1em;
}

```

```{r, results='asis'}
# Run basic linear models for both continuous and binary outcome
lm.willing_to_pay <- lm(willing_to_pay ~ subgroup, data=df_finished)
lm.is_willing_to_pay <- lm(is_willing_to_pay ~ subgroup, data = df_finished)

stargazer(lm.willing_to_pay,lm.is_willing_to_pay, title = "Effect of Information Warning on Privacy",
          align = TRUE,
          dep.var.labels = c("Willing to pay","Is Willing to Pay"),
          column.labels = c("(Continuous)","(Binary)"),
          covariate.labels = c("Low Info (Treatment 1)", "Medium Info (Treatment 2)", "High Info (Treatment 3)"),
          type = "html"
         )
```

### Heterogeneous Treatment Effects
```{r, results='asis'}
# Run linear model for heterogeneous treatment effects for Age >= 35
lm.willing_to_pay.hetero <- lm(willing_to_pay ~ subgroup + equal_over35 + subgroup:equal_over35, data=df_finished)
lm.is_willing_to_pay.hetero <- lm(is_willing_to_pay ~ subgroup + equal_over35 + subgroup:equal_over35, data = df_finished)

stargazer(lm.willing_to_pay, lm.willing_to_pay.hetero, lm.is_willing_to_pay, lm.is_willing_to_pay.hetero, title = "Effect of Information Warning on Privacy",
          align = TRUE,
          dep.var.labels = c("Willing to pay","Is Willing to Pay"),
          column.labels = c("(Continuous)","(Continuous)","(Binary)","(Binary)"),
          covariate.labels = c("Low Info (Treatment 1)", "Medium Info (Treatment 2)", "High Info (Treatment 3)",
                               "Age 35+", "Low Info and Age 35+", "Medium Info and Age 35+", "High Info and Age 35+"),
          type = "html"
          )
```
Interaction Coefficients are not statistically significant, suggesting there are no Heterogeneous Treatment Effects
```{r, results='asis'}
# Run linear model for heterogeneous treatment effects for Age >= 30
lm.willing_to_pay.hetero <- lm(willing_to_pay ~ subgroup + equal_over30 + subgroup:equal_over30, data=df_finished)
lm.is_willing_to_pay.hetero <- lm(is_willing_to_pay ~ subgroup + equal_over30 + subgroup:equal_over30, data = df_finished)

stargazer(lm.willing_to_pay, lm.willing_to_pay.hetero, lm.is_willing_to_pay, lm.is_willing_to_pay.hetero, title = "Effect of Information Warning on Privacy",
          align = TRUE,
          dep.var.labels = c("Willing to pay","Is Willing to Pay"),
          column.labels = c("(Continuous)","(Continuous)","(Binary)","(Binary)"),
          covariate.labels = c("Low Info (Treatment 1)", "Medium Info (Treatment 2)", "High Info (Treatment 3)",
                               "Age 30+", "Low Info and Age 30+", "Medium Info and Age 30+", "High Info and Age 30+"),
          type = "html")
```
Interaction Coefficients are not statistically significant, suggesting there are no Heterogeneous Treatment Effects
```{r, results='asis'}
# Run linear model for heterogeneous treatment effects for Graduate Degree
lm.willing_to_pay.hetero <- lm(willing_to_pay ~ subgroup + hasGraduateDegree + subgroup:hasGraduateDegree, data=df_finished)
lm.is_willing_to_pay.hetero <- lm(is_willing_to_pay ~ subgroup + hasGraduateDegree + subgroup:hasGraduateDegree, data = df_finished)

stargazer(lm.willing_to_pay, lm.willing_to_pay.hetero, lm.is_willing_to_pay, lm.is_willing_to_pay.hetero, title = "Effect of Information Warning on Privacy",
          align = TRUE,
          dep.var.labels = c("Willing to pay","Is Willing to Pay"),
          column.labels = c("(Continuous)","(Continuous)","(Binary)","(Binary)"),
          covariate.labels = c("Low Info (Treatment 1)", "Medium Info (Treatment 2)", "High Info (Treatment 3)",
                               "Has Graduate Degree", "Low Info and Has Graduate Degree", 
                               "Medium Info and Has Graduate Degree", "High Info and Has Graduate Degree"),
          type = "html")
```